fdcoexist

### 2018-08-25 paper_simulations.Rmd
:sparkles: fct automatic labelling of scenars + simpler scenars

# Define scenarios -------------------------------------------------------------
# Scenarios on traits affecting growth and competition
trait_scenarios = list(
    RA00     = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(1, 0, 0),
                          compet_weight = c(0, 0, 1)),
    RA1090   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.90, 0.10, 0),
                          compet_weight = c(0,    0.90, 0.10)),
    RA2575   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.75, 0.25, 0),
                          compet_weight = c(0,    0.75, 0.25)),
    RA5050   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.5, 0.5, 0),
                          compet_weight = c(0,   0.5, 0.5)),
    RA7525   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.25, 0.75, 0),
                          compet_weight = c(0,    0.25, 0.75)),
    RA9010   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.10, 0.90, 0),
                          compet_weight = c(0,    0.10, 0.90)),
    RA100100 = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0, 1, 0),
                          compet_weight = c(0, 1, 0))
)

@@

trait_scenar_names = c(
    RA00   = "Growth = 0%\nCompet. = 0%",
    RA1090 = "Growth = 10%\nCompet. = 90%",
    RA2575 = "Growth = 25%\nCompet. = 75%",
    RA5050 = "Growth = 50%\nCompet. = 50%",
    RA7525 = "Growth = 75%\nCompet. = 25%",
    RA9010 = "Growth = 90%\nCompet. = 10%",
    RA100100 = "Growth = 100%\nCompet. = 100%"
)

# Graphical functions ----------------------------------------------------------
facet_scenar = facet_wrap(vars(scenario),
                          labeller = as_labeller(trait_scenar_names))

@@

# Plot the relationship between patch CWMs along the environment considering
# total abundance
fig_cwm_env_abund = function(simul_df, simul_label, n_bins = 24,
                             given_trans = "identity") {
    simul_df %>%
        group_by(scenario, patch) %>%
        summarise_at(vars(contains("cwm"), N), sum) %>%
        mutate(patch_optim = gsub("patches", "", patch) %>%
                   as.numeric()) %>%
        gather("cwm_name", "cwm_value", contains("cwm")) %>%
        ungroup() %>%
        ggplot(aes(patch_optim, cwm_value, z = N)) +
        stat_summary_2d(bins = n_bins) +
        facet_grid(vars(scenario), vars(cwm_name),
                   labeller = labeller(scenario = trait_scenar_names,
                                       cwm_name = label_value)) +
        scale_fill_viridis_c(trans = given_trans, option = "E") +
        labs(x = "Environment",
             y = "Community-Weighted Mean (CWM)",
             fill = "Total Abundance",
             subtitle = simul_label) +
        theme(legend.position = "top")
}

@@

    ggplot(simul_df2 %>%
               filter(N > 0),
           aes(patch_optim, trait_value, z = N)) +
        stat_summary_2d(geom = "raster", bins = n_bins, interpolate = TRUE) +
        geom_line(aes(patch_optim, cwm, color = "firebrick"), size = 1) +
        facet_grid(vars(scenario), vars(trait_name),
                   labeller = labeller(scenario = trait_scenar_names,
                                       trait_name = function(x) gsub("_", " ",
                                                                     x))) +
        scale_fill_viridis_c(trans = given_trans, option = "E") +
        scale_color_manual(name = "CWM", values = c(firebrick = "grey80"),
                           labels = "") +
        labs(x = "Environment",
             y = "Trait Value",
             fill = "Species Abundance",
             subtitle = simul_label) +
        guides(colour = guide_legend(override.aes = list(size = 1,
                                                         color = "grey50"))) +
        theme(legend.position = "top")
}
```

>>>>

# Define scenarios -------------------------------------------------------------
# Scenarios on traits affecting growth and competition
trait_scenarios = list(
    R0A0 = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(1, 0, 0),
                          compet_weight = c(0, 0, 1)),
    R0A100 = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(1, 0, 0),
                          compet_weight = c(0, 1, 0)),
    R10A90   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.90, 0.10, 0),
                          compet_weight = c(0,    0.90, 0.10)),
    R25A75   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.75, 0.25, 0),
                          compet_weight = c(0,    0.75, 0.25)),
    R50A50   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.5, 0.5, 0),
                          compet_weight = c(0,   0.5, 0.5)),
    R75A25   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.25, 0.75, 0),
                          compet_weight = c(0,    0.25, 0.75)),
    R90A10   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.10, 0.90, 0),
                          compet_weight = c(0,    0.10, 0.90)),
    R100A0   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0, 1, 0),
                          compet_weight = c(0, 0, 1)),
    R100A100 = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0, 1, 0),
                          compet_weight = c(0, 1, 0))
)

@@

# Graphical functions ----------------------------------------------------------
label_scenar_facets = function(scenar_name) {
    scenar_name %>%
        as.character() %>%
        str_remove("R") %>%
        str_split("A") %>%
        map_chr(~paste0("Growth = ",  .x[1], "%\n",
                        "Compet. = ", .x[2], "%"))
}

facet_scenar = facet_wrap(vars(scenario),
                          labeller = labeller(scenario = label_scenar_facets))

@@

# Plot the relationship between patch CWMs along the environment considering
# total abundance
fig_cwm_env_abund = function(simul_df, simul_label, n_bins = 24,
                             given_trans = "identity") {
    simul_df %>%
        group_by(scenario, patch) %>%
        summarise_at(vars(contains("cwm"), N), sum) %>%
        mutate(patch_optim = gsub("patches", "", patch) %>%
                   as.numeric()) %>%
        gather("cwm_name", "cwm_value", contains("cwm")) %>%
        ungroup() %>%
        ggplot(aes(patch_optim, cwm_value, z = N)) +
        stat_summary_2d(bins = n_bins) +
        facet_grid(vars(scenario), vars(cwm_name),
                   labeller = labeller(scenario = label_scenar_facets,
                                       cwm_name = label_value)) +
        scale_fill_viridis_c(trans = given_trans, option = "E") +
        labs(x = "Environment",
             y = "Community-Weighted Mean (CWM)",
             fill = "Total Abundance",
             subtitle = simul_label) +
        theme(legend.position = "top")
}

@@

    ggplot(simul_df2 %>%
               filter(N > 0),
           aes(patch_optim, trait_value, z = N)) +
        stat_summary_2d(geom = "raster", bins = n_bins, interpolate = TRUE) +
        geom_line(aes(patch_optim, cwm, color = "firebrick"), size = 1) +
        facet_grid(vars(scenario), vars(trait_name),
                   labeller = labeller(scenario = label_scenar_facets,
                                       trait_name = function(x) gsub("_", " ",
                                                                     x))) +
        scale_fill_viridis_c(trans = given_trans, option = "E") +
        scale_color_manual(name = "CWM", values = c(firebrick = "grey80"),
                           labels = "") +
        labs(x = "Environment",
             y = "Trait Value",
             fill = "Species Abundance",
             subtitle = simul_label) +
        guides(colour = guide_legend(override.aes = list(size = 1,
                                                         color = "grey50"))) +
        theme(legend.position = "top")
}
```
